Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-04-27 paper/referee_report_1/response.md

13. There was no detection in the two 20-min MWA observations made via periodicity search. A few pulsars were reported to exhibit sporadic, strong single pulses coexisting with a periodic weak emission in the duration of weak mode (e.g. PSR B0826-34). Does J0026-1956 has the similar emission behavior? You'd better try single-pulse search technique on the two observations.

  * We formed pulsestacks of the two 20-min observations and found a small amount of relatively faint emission in them that is just visible in the pulse stack. Accordingly, we have promoted these two observations to the same standing as the original four, included them in Table 1 and Figure 2, and performed all the same analyses on them. The lack of significant emission in these two observations means that the main conclusions of our nulling analysis are essentially unchanged. There are many places throughout the text that have been updated accordingly, which are marked in bold as usual.

14. The LRFS in Figure 6 clearly presents the drifting feature at a frequency of ~0.03 cycles/period in the on-pulse window. In addition, a wide modulation feature with frequency ranging from 0.05-0.1 cycles/period is detected in the leading emission component. The corresponding feature with weak power in the 2DFS is also discernible.

  * These extra details are now more explicitly spelled out in the caption to the LRFS/2DFS figure. We have also expanded slightly on the interpretation of the diffuse component (as a possible connection to Mode B) in the last part of Section 3.2.4.

### 2022-04-27 paper/main.tex
Answered a couple more of the referee's points

Fluctuation spectra are most useful when the drift bands are regularly spaced (i.e.\ when $P_3$ is constant).
The fact that this is clearly not the case for \psr{} means that features in the fluctuation spectra will be spread out over a range of spectral bins.
Fig. \ref{fig:lrfs} shows the longitude-resolved fluctuation spectrum (LRFS) and the two-dimensional fluctuation spectrum (2DFS) for the drift sequence shown in Fig. \ref{fig:A2_example}.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{A2_lrfs.png} \\
    \includegraphics[width=0.45\textwidth]{A2_tdfs.png}
    \caption{\textit{Top:} The LRFS computed on the section of the pulsestack shown in Fig. \ref{fig:A2_example}. \textit{Bottom:} A zoomed section of the 2DFS of the same pulsestack section.}
    \label{fig:lrfs}
\end{figure}
Despite the changing $P_3$ and the relative disorganization of the drift rate, the LRFS and 2DFS show surprisingly high-Q features at $P_3 \approx 33 \pm 4\,P$ and $P_2 \approx 16^\circ \pm 2^\circ$, which are consistent with the fitted model values of $P_3$ changing from $\sim50\,P$ to $27\,P$ throughout the sequence, and $P_2 = 13.8^\circ \pm 0.3^\circ$.
The relative lack of power in the LRFS (bottom panel) near phase $\sim2^\circ$ is likely related to the interruptions in the organization of the drift bands that occur at that phase, discussed in the previous section.

>>>>

Fluctuation spectra are most useful when the drift bands are regularly spaced (i.e.\ when $P_3$ is constant).
The fact that this is clearly not the case for \psr{} means that features in the fluctuation spectra will be spread out over a range of spectral bins.
Fig. \ref{fig:lrfs} shows the longitude-resolved fluctuation spectrum (LRFS) and the two-dimensional fluctuation spectrum (2DFS) for the drift sequence shown in Fig. \ref{fig:A2_example}.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{A2_lrfs.png} \\
    \includegraphics[width=0.45\textwidth]{A2_tdfs.png}
    \caption{\textit{Top:} The LRFS computed on the section of the pulsestack shown in Fig. \ref{fig:A2_example}. \textit{Bottom:} A zoomed section of the 2DFS of the same pulse stack section. {\bf The feature at $\sim0.03\,$cycles/$P$ corresponds to $P_3 \approx 33 \pm 4\,P$, consistent with the average $P_3$ of this sequence determined from the pulse stack directly. The more diffuse power in the range $0.05$-$0.1\,$cycles/$P$ in the leading component (and the corresponding feature visible in the 2DFS) are indicative of the relative disorganization of the drift bands that occurs there.}}
    \label{fig:lrfs}
\end{figure}
Despite the changing $P_3$ and the relative disorganization of the drift rate, the LRFS and 2DFS show surprisingly high-Q features at $P_3 \approx 33 \pm 4\,P$ and $P_2 \approx 16^\circ \pm 2^\circ$, which are consistent with the fitted model values of $P_3$ changing from $\sim50\,P$ to $27\,P$ throughout the sequence, and $P_2 = 13.8^\circ \pm 0.3^\circ$.
The relative lack of power in the {\bf bottom panel of the LRFS} near phase $\sim2^\circ$ is likely related to the interruptions in the organization of the drift bands that occur at that phase, discussed in the previous section.
{\bf Interestingly, the presence of extra power in the LRFS in the leading component between $0.05$-$0.1\,$cycles/$P$ is suggestive of a connection to Mode B, which (with its $P_3 \approx 10\,P$) would be expected to contribute power in the LRFS near this range.}
